Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2021-03-02 summary.Rmd
typo

**Theorem 2** (Generalization to $K > 2$). There exists a block diagonal matrix 
$X \in \mathbb{R}^{n \times K^2}$ defined by PABM parameters 
$\{\lambda^{(kl)}\}_K$ and $U \in \mathbb{R}^{K^2 \times K^2}$ that is fixed 
for each $K$ such that $A \sim GRDPG_{K (K+1) / 2, K (K-1) / 2}(XU)$ and 
$A \sim PABM(\{(\lambda^{(kl)}\})_K)$ are equivalent.

>>>>

**Theorem 2** (Generalization to $K > 2$). There exists a block diagonal matrix 
$X \in \mathbb{R}^{n \times K^2}$ defined by PABM parameters 
$\{\lambda^{(kl)}\}_K$ and orthonormal matrix 
$U \in \mathbb{R}^{K^2 \times K^2}$ that is fixed 
for each $K$ such that $A \sim GRDPG_{K (K+1) / 2, K (K-1) / 2}(XU)$ and 
$A \sim PABM(\{(\lambda^{(kl)}\})_K)$ are equivalent.
